The role of advection versus diffusion in intraventricular transport

### 2025-03-06 paper/main.tex
Shuffle structure.
And move Discussion

\title{The role of advection versus diffusion in intraventricular transport}
%
\maketitle
%
% Author: Please give full first and last names for authors and
% include * after the name of all corresponding authors
%
\author{Halvor Herlyng*},
\author{Ada J.~Ellingsrud},
\author{Miroslav Kuchta},
\author{Inyoung Jeong},
\author{Marie E.~Rognes}, 
\author{Nathalie Jurisch-Yaksi*}

@@

% Experimental section
\section{Computational Methods}
\subsection{Image-based computational geometries of zebrafish brain ventricles}
To model flow and transport in zebrafish larval brain ventricles, we generated a
3D representation of the brain ventricular walls using confocal imaging data of a zebrafish embryo
injected intraventricularly with a 70 kDa dye at 2 dpf~\cite{Olstad2019CiliaryDevelopment}. 
From the imaging data, we constructed a computational mesh of the ventricles (\Crefpanels{fig:fig1}{d}).
The interior volume was meshed with fTetWild~\cite{Hu2020FastWild}. 
The standard mesh consisted of 132 134 tetrahedral cells and had a
maximal (minimal) edge length of 14.9 \textmu m (4.68 \textmu m). 
At 2 dpf, the ventricular system consists mainly of 3 cavities: the telencephalic (anterior),
the di-/mesencephalic (middle) and the rhombencephalic (posterior) ventricles,
which are connected by interventricular ducts. 
Parts of the ventricular surfaces were marked to be lined with
motile cilia (\Crefpanels{fig:fig1}{d}, magenta markers)~\cite{Olstad2019CiliaryDevelopment}.
\begin{figure}%[hbt!]
    \centering
    \includegraphics[width=\linewidth]{graphics/figure1.png}
    \caption{
    \textbf{a.} Schematic illustration of the two cerebrospinal fluid (CSF) flow components modeled,
    motile cilia and cardiac pulsations, and their contributions to the flow patterns.
    \textbf{b.} Particle tracking data visualizing flow directionality in the middle ventricle.
    \textbf{c.} Flow velocity magnitudes in the middle ventricle from particle tracking data.
    \textbf{d.} Computational mesh with marked facets indicating regions of motile cilia (magenta) and
    anterior/posterior facets (blue).
    \textbf{e.} Streamlines of the (steady-state) CSF flow field simulated with the
    cilia-only/no-cardiac flow model.
    \textbf{f.} Streamlines of the CSF flow field simulated with the cardiac-only/no-cilia flow
    model at a time 25\% into the cardiac cycle. %t=0.112613 s, period=0.45045 s
    \textbf{g.} Streamlines simulated with the baseline flow model at
    a time 25\% into the cardiac cycle. %t=0.112613 s
    \textbf{h.} Streamlines simulated with the baseline flow model at
    a time 50\% into the cardiac cycle. %t=0.225225 s
    \textbf{i.} Streamlines simulated with the baseline flow model at
    a time 75\% into the cardiac cycle. %t=0.315315 s
    \textbf{j.} Illustration of the cardiac-related normal pressure forcing imposed on the
    anterior/posterior boundaries. Time instants of panels \textbf{f, h--j} are indicated.
    }
    \label{fig:fig1}
\end{figure}

%%------PHYSICAL EXPERIMENTS------%%
\section{Experimental Methods}
\subsection{Zebrafish maintenance, genotyping and strains in photoconversion experiments}
The animal facilities for zebrafish~(\emph{danio rerio}) are approved by the
Norwegian Food Safety Authority (NFSA, Mattilsynet).
The zebrafish were maintained in accordance with the guidelines set by the
NFSA and the European Communities Council Directive.

@@

\section{Conclusion}
We have presented a numerical model
of cerebrospinal fluid flow and solute transport in
zebrafish brain ventricles based on finite element methods.
A realistic ventricular geometry from medical imaging was used to perform a
computational study. The flow model reproduces
the experimentally observed flow features of cilia-mediated cerebrospinal fluid
flow in zebrafish brain ventricles. Coupling the flow to the transport model,
we estimated how slowly or rapidly molecules of varying size are transported in
the ventricles. 
The numerical model was validated with in vivo experiments, measuring the movement of
a photoconverted fluorescent protein in zebrafish brain ventricles,
both for healthy animals and mutant animals with ciliary dysfunction.
We observed good alignment between computational and experimental results.
Simulations indicate that cilia-driven advection is important
for transport of larger molecules, whereas diffusion accounts for most of
the transport of smaller molecules. 
Experimental results support the conclusion that cilia only affect the
local distribution of small proteins,
while most of their transport is governed by diffusion.

>>>>

\title{The role of advection versus diffusion in intraventricular transport}
%
\maketitle
 %
% Author: Please give full first and last names for authors and
% include * after the name of all corresponding authors

\author{Halvor Herlyng*},
\author{Ada J.~Ellingsrud},
\author{Miroslav Kuchta},
\author{Inyoung Jeong},
\author{Marie E.~Rognes}, 
\author{Nathalie Jurisch-Yaksi*}

@@

\begin{figure}%[hbt!]
    \centering
    \includegraphics[width=\linewidth]{graphics/figure1.png}
    \caption{
    \textbf{a.} Schematic illustration of the two cerebrospinal fluid (CSF) flow components modeled,
    motile cilia and cardiac pulsations, and their contributions to the flow patterns.
    \textbf{b.} Particle tracking data visualizing flow directionality in the middle ventricle.
    \textbf{c.} Flow velocity magnitudes in the middle ventricle from particle tracking data.
    \textbf{d.} Computational mesh with marked facets indicating regions of motile cilia (magenta) and
    anterior/posterior facets (blue).
    \textbf{e.} Streamlines of the (steady-state) CSF flow field simulated with the
    cilia-only/no-cardiac flow model.
    \textbf{f.} Streamlines of the CSF flow field simulated with the cardiac-only/no-cilia flow
    model at a time 25\% into the cardiac cycle. %t=0.112613 s, period=0.45045 s
    \textbf{g.} Streamlines simulated with the baseline flow model at
    a time 25\% into the cardiac cycle. %t=0.112613 s
    \textbf{h.} Streamlines simulated with the baseline flow model at
    a time 50\% into the cardiac cycle. %t=0.225225 s
    \textbf{i.} Streamlines simulated with the baseline flow model at
    a time 75\% into the cardiac cycle. %t=0.315315 s
    \textbf{j.} Illustration of the cardiac-related normal pressure forcing imposed on the
    anterior/posterior boundaries. Time instants of panels \textbf{f, h--j} are indicated.
    }
    \label{fig:fig1}
\end{figure}

@@

%\section{Conclusion}
In conclusion, we have presented a numerical model
of cerebrospinal fluid flow and solute transport in
zebrafish brain ventricles based on finite element methods.
A realistic ventricular geometry from medical imaging was used to perform a
computational study. The flow model reproduces
the experimentally observed flow features of cilia-mediated cerebrospinal fluid
flow in zebrafish brain ventricles. Coupling the flow to the transport model,
we estimated how slowly or rapidly molecules of varying size are transported in
the ventricles. 
The numerical model was validated with in vivo experiments, measuring the movement of
a photoconverted fluorescent protein in zebrafish brain ventricles,
both for healthy animals and mutant animals with ciliary dysfunction.
We observed good alignment between computational and experimental results.
Simulations indicate that cilia-driven advection is important
for transport of larger molecules, whereas diffusion accounts for most of
the transport of smaller molecules. 
Experimental results support the conclusion that cilia only affect the
local distribution of small proteins,
while most of their transport is governed by diffusion.

\section{Methods}

\subsection{Zebrafish maintenance, genotyping and strains in photoconversion experiments}
The animal facilities for zebrafish~(\emph{danio rerio}) are approved by the
Norwegian Food Safety Authority (NFSA, Mattilsynet).
The zebrafish were maintained in accordance with the guidelines set by the
NFSA and the European Communities Council Directive.

\subsection{Image-based computational geometries of zebrafish brain ventricles}
To model flow and transport in zebrafish larval brain ventricles, we generated a
3D representation of the brain ventricular walls using confocal imaging data of a zebrafish embryo
injected intraventricularly with a 70 kDa dye at 2 dpf~\cite{Olstad2019CiliaryDevelopment}. 
From the imaging data, we constructed a computational mesh of the ventricles (\Crefpanels{fig:fig1}{d}).
The interior volume was meshed with fTetWild~\cite{Hu2020FastWild}. 
The standard mesh consisted of 132 134 tetrahedral cells and had a
maximal (minimal) edge length of 14.9 \textmu m (4.68 \textmu m). 
At 2 dpf, the ventricular system consists mainly of 3 cavities: the telencephalic (anterior),
the di-/mesencephalic (middle) and the rhombencephalic (posterior) ventricles,
which are connected by interventricular ducts. 
Parts of the ventricular surfaces were marked to be lined with
motile cilia (\Crefpanels{fig:fig1}{d}, magenta markers)~\cite{Olstad2019CiliaryDevelopment}.

%%------PHYSICAL EXPERIMENTS------%%
%\section{Experimental Methods}
